OneD: increasing reproducibility of Hi-C Samples with abnormal karyotypes

### 2018-01-16 manuscript_nar.tex
Updating references and sources

We gathered a set of published Hi-C data \citep[][BioRxiv:
https://doi.org/10.1101/132456]{ledily2014distinct, encode2012integrated,
rao20143d, lin2012global, dixon2012topological} and unpublished data of
different cell types and organisms (Supplementary Table~1).

@@

All data were processed through a pipeline based on TADbit
\citep{serra2016structural}. Briefly, after controlling the quality of
FASTQ files, paired-end reads were mapped to the corresponding reference
genome (hg38 or mm10) taking into account the restriction enzyme site.
Non-informative contacts were removed applying the following TADbit
filters: \texttt{self-circle}, \texttt{dangling-ends}, \texttt{error},
\texttt{extra-dangling-ends}, \texttt{duplicated} and
\texttt{random-breaks} (for more details see BioRxiv:
https://doi.org/10.1101/132456). In addition, the pipeline is available
from the Supplementary Material published by \cite{quilez2017managing}.

>>>>

We gathered a set of published Hi-C data
\citep{stadhouders2018transcription,ledily2014distinct,encode2012integrated,rao20143d,lin2012global,dixon2012topological}
and unpublished data of different cell types and organisms (Supplementary
Table~1).

@@

All data were processed through a pipeline based on TADbit
\citep{serra2016structural}. Briefly, after controlling the quality of FASTQ
files, paired-end reads were mapped to the corresponding reference genome (hg38
or mm10) taking into account the restriction enzyme site.  Non-informative
contacts were removed applying the following TADbit filters:
\texttt{self-circle}, \texttt{dangling-ends}, \texttt{error},
\texttt{extra-dangling-ends}, \texttt{duplicated} and \texttt{random-breaks}
(for more details see \cite{stadhouders2018transcription}). In addition, the
pipeline is available from the Supplementary Material published by
\cite{quilez2017managing}.
